models with mice

### 2024-03-17 withmice.Rmd
mifa for coal and solar

>>>>

# NUCLEAR2 : only charcateristics of tech

ecopoln2 <- formice1 %>%
  dplyr::select(
    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
    RELYNUCLEAR, age, urban_rural, gender, caste, religion, State
  )

str(ecopoln2)
md.pattern(ecopoln2) #the variables with missing values:

mcar_test(data=ecopoln2)
```

# Nuclear2 : Mifa for new eco-pol value scale

miecopoln2 <- mifa(data= ecopoln2,
                cov_vars = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=10,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 528,)

miecopoln2

ecopolfitn2 <- psych::fa(miecopoln2$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(ecopolfitn2, sort= TRUE, cut= 0.4)

# Solar : MAR condition and missing data pattern

ecopols <- formice1 %>%
  dplyr::select(
    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
    DISPLACESOLAR,  POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR,
    PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR,
    RELYSOLAR,age, urban_rural, gender, caste, religion, State
  )

md.pattern(ecopols) #the variables with missing values:

mcar_test(data=ecopols)
```

# Solar : Mifa for new eco-pol value scale

miecopols <- mifa(data= ecopols,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=5,
                n_pc= 1:2,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 528,)

miecopols

ecopolfits <- psych::fa(miecopols$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(ecopolfits, sort= TRUE, cut= 0.4)

# Solar 2 : only charcateristics of tech

ecopols2 <- formice1 %>%
  dplyr::select(
    DISPLACESOLAR,  POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR,
    PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR,
    RELYSOLAR, age, urban_rural, gender, caste, religion, State
  )

str(ecopols2)
md.pattern(ecopols2) #the variables with missing values:

mcar_test(data=ecopols2)
```

# SOLAR2 : Mifa for new eco-pol value scale

miecopols2 <- mifa(data= ecopols2,
                cov_vars = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=10,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 528,)

miecopols2

ecopolfits2 <- psych::fa(miecopols2$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(ecopolfits2, sort= TRUE, cut= 0.4)

# Solar: Mifa with CFA

## CFA on ecopol vars for solar energy

ecopols_2fa <- '
  Ndevelop =~ DEVSOLAR + PRIDESOLAR + NPRIDESOLAR + PROSPERSOLAR + JOBSSOLAR 
  Pdevelop =~ HEALTHSOLAR + BEAUTYSOLAR + DISPLACESOLAR + POLLUTESOLAR + ENVOVERDEV
'

secopol_cfa <- cfa(ecopols_2fa, data = miecopols$cov_combined, std.lv = TRUE)
summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)

# COAL : MAR condition and missing data pattern

ecopolc <- formice1 %>%
  dplyr::select(
    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
    DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,
    PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,
    RELYCOAL,age, urban_rural, gender, caste, religion, State
  )

md.pattern(ecopolc) #the variables with missing values:

mcar_test(data=ecopolc)
```

# Coal : Mifa for new eco-pol value scale

miecopolc <- mifa(data= ecopolc,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=50,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 528,)

miecopolc

ecopolfitc <- psych::fa(miecopolc$cov_combined, nfactors = 3, rotate = "varimax")

print.psych(ecopolfitc, sort= TRUE, cut= 0.4)

# COAL2 : only charcateristics of tech

ecopolc2 <- formice1 %>%
  dplyr::select(
    DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,
    PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,
    RELYCOAL,age, urban_rural, gender, caste, religion, State
  )

md.pattern(ecopolc2) #the variables with missing values:

mcar_test(data=ecopolc2)
```

# Coal2 : Mifa for new eco-pol value scale

miecopolc2 <- mifa(data= ecopolc2,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=5,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 528,)

miecopolc2

ecopolfitc2 <- psych::fa(miecopolc2$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)

cor.plot(ecopolc %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))
```

# Coal: Mifa with CFA

# (DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,DISPLACECOAL,  POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL,PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL,RELYCOAL)

## CFA on ecopol vars for coal

ecopolc_2fa <- '
  Pride =~ PRIDECOAL + NPRIDECOAL + DEVOVERENV +  DECISIONCEN + OWNERPVT + DECISIONCEN  + OWNERNOREG + ECONOMYGLOBAL
  Social Costs =~ BEAUTYCOAL + POLLUTECOAL + HEALTHCOAL
  Social Costs2 =~ OWNERPUB + ENVOVERDEV + DISPLACECOAL

'

cecopol_cfa <- cfa(ecopolc_2fa, data = miecopolc$cov_combined, std.lv = TRUE)
summary(cecopol_cfa, fit.measure= TRUE, standardized = TRUE)
